Learning \strips\ Action Models from State-Constraints

### 2018-01-04 doc/ijcai-18/constraints-learning.tex
AMAN reference added to ijcai18 paper

The Machine Learning of planning action models is a promising alternative to hand-coding them and nowadays, there exist sophisticated algorithms like {\sc ARMS}~\cite{yang2007learning}, {\sc SLAF}~\cite{amir:alearning:JAIR08} or {\sc LOCM}~\cite{cresswell2013acquiring}. Motivated by recent advances on the synthesis of different kinds of generative models with classical planning~\cite{bonet2009automatic,segovia2016hierarchical,segovia2017generating}, this paper introduces an innovative approach for learning \strips\ action models that:
\begin{enumerate}
\item Is defined as a classical planning compilation, which opens the door to the {\em bootstrapping} of planning action models.
\item Does not require observations of the particular executed actions. An off-the-shelf classical planner leverages on the given constraints to determine the executed actions.
\item Can assess the learned \strips\ models with respect to a {\em reference model}, even when learning is so low constrained that actions are reformulated and still compliant with the learning inputs. 
\end{enumerate}

>>>>

The Machine Learning of planning action models is a promising alternative to hand-coding them and nowadays, there exist sophisticated algorithms like {\sc AMAN}~\cite{zhuo2013action}, {\sc ARMS}~\cite{yang2007learning}, {\sc SLAF}~\cite{amir:alearning:JAIR08} or {\sc LOCM}~\cite{cresswell2013acquiring}. Motivated by recent advances on the synthesis of different kinds of generative models with classical planning~\cite{bonet2009automatic,segovia2016hierarchical,segovia2017generating}, this paper introduces an innovative approach for learning \strips\ action models that:
\begin{enumerate}
\item Is defined as a classical planning compilation, which opens the door to the {\em bootstrapping} of planning action models.
\item Does not require observations of the particular executed actions. An off-the-shelf classical planner leverages on the given constraints to determine the executed actions.
\item Can assess the learned \strips\ models with respect to a {\em reference model}, even when learning is so low constrained that actions are reformulated and still compliant with the learning inputs. 
\end{enumerate}
